Dependent Object Types

### 2012-07-02 doc/semester/report.tex
slide progress

The terms in DOT consists of variables $x$, $y$, $z$, lambda
abstractions $\abs x T t$, function application $\app t t'$, field
selections $t.l$ and object creation expressions $\new x c t$, where
$c$ is a constructor $T_c \ldefs{\seq{l = v}}$.

>>>>

The terms in DOT consists of variables $x$, $y$, $z$, lambda
abstractions $\abs x T t$, function application $\app t {t'}$, field
selections $t.l$ and object creation expressions $\new x c t$, where
$c$ is a constructor $T_c \ldefs{\seq{l = v}}$.
